Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-05-03 PAPER.tex
minor text change

In addition to mitigating foreground bias at high-$k$'s, two other sources of bias that we actively suppress in the PAPER-64 
analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``even" with ``even", for 
example, in order to prevent the squaring of the same thermal noise.

>>>>

In addition to mitigating foreground bias at high-$k$'s, two other sources of bias that we actively suppress in the PAPER-64 
analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``baseline 1" with ``baseline 1", for 
example, in order to prevent the squaring of the same thermal noise.
